\documentclass[11pt,a4paper,sans]{moderncv}

\moderncvstyle{banking}
\moderncvcolor{black}
\nopagenumbers{}
\usepackage[utf8]{inputenc}
\usepackage{ragged2e}
\usepackage[scale=0.915]{geometry}
\usepackage{import}
\usepackage{multicol}
\usepackage{import}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\name{Gokul}{Narayanan}
\newcommand*{\customcventry}[7][.13em]{
\begin{tabular}{@{}l}
{\bfseries #4} \
{\itshape #3}
\end{tabular}
\hfill
\begin{tabular}{l@{}}
{\bfseries #5} \
{\itshape #2}
\end{tabular}
\ifx&#7&%
\else{\
\begin{minipage}{\maincolumnwidth}%
\small#7%
\end{minipage}}\fi%
\par\addvspace{#1}}
\begin{document}
\makecvtitle
\vspace*{-16mm}
\begin{center}\textbf{Software engineer}\end{center}
\begin{center}
\begin{tabular}{ c c c }
\faMobile\enspace +91 7304225266 & \enspace gokul.narayanan@pm.me & \faHome\enspace Kannur, Kerala\\
\faLinkedin\enspace \color{blue} \href{https://www.linkedin.com/in/gokul-narayanan-5a7681210/}{in/gokul-narayanan } & \enspace &
\faGithub\enspace \color{blue} \href{https://github.com/narayanan-gokul}{github.com/narayanan-gokul}
\end{tabular}
\end{center}

\section{Profile}
{Dedicated Software developer with an ability to work on well-defined objectives religiously and independently. Proficient at learning and honing new skills in the shortest time frame possible. Skilled at deep diving into, understanding, and implementing concepts.}

\section{Professional Experience}
\customcventry{07/2024 ‐ present}{{{(Freelance)}}}{Software Developer,}{Remote}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Developed node.js scripts for fetching market data using websockets.
\item Developing a web app with backend written in Golang and frontend in HTMX.
\end{itemize}}}

\customcventry{05/2023 ‐ 05/2024}{{{(Codeinbound LLP)}}}{Software Development Engineer,}{Remote}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Implemented user management functionality such as authorization for a network monitoring system.
\item Developed an entire reporting module from the ground up, providing users with the ability to visualize their data immediately on request or have it sent to them periodically.
\item Design of the reporting module allows data to be aggregated from any part of the application's dataset.
\item Created SQL functions for custom aggregation of data based on the reporting requirements.
\end{itemize}}}

\customcventry{02/2023 ‐ 05/2023}{{{(Codeinbound LLP)}}}{Software Development Engineer Intern,}{Remote}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Developed basic entities and their relations for multiple aspects of a network monitoring system.
\item Created and tested more than 10 entities pertaining to various functionalities.
\item Worked on creating and validating database migrations for above entities.
\item Created URL route handlers for basic CRUD functionality of the application.
\end{itemize}}}



\section{Education}
\customcventry{}{{Fr. C Rodrigues Institute of Technology}}{BE Electrical Engineering}{Vashi, Navi Mumbai}{}{}{}

\section{Skills}
{\begin{itemize}[label=\textbullet]
\item {\textbf{Programming languages:} Javascript, Typescript, SQL, Java, Python, Golang}
\item {\textbf{Frameworks and libraries:} NestJS, TypeORM, FastAPI. SQLAlchemy, Alembic, HTMX}
\item {\textbf{Technologies:} Linux, Redis, Message queues, Puppeteer, Nodejs, PostgreSQL}
\end{itemize}}

\section{Projects}
{
\customcventry{}{{{}}}{Software suite for a vritual hardware platform called Hack}{}{}{
(A part of the Nand2tetris course (part 1) offered by the Hebrew University of Jerusalem on Coursera)
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Developed an assembler and a VM (Virtual Machine) translator in Java for the hack platform.
\item The VM translator acts as a backend for the compiler for a basic object oriented language called 'Jack'.
\item The translator converts instructions written in a VM language to assembly instructions that can be run on the hack platform.
\end{itemize}}}
}
\end{document}
