\documentclass[11pt]{article}
\usepackage[a4paper,margin=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{array}
\usepackage{tabularx}
\usepackage{nopageno}
\setlength{\parindent}{0pt}
\setlist[itemize]{noitemsep, topsep=0pt}

\begin{document}

\begin{tabularx}{\textwidth}{ll}
	{\LARGE \textbf{Gokul Narayanan}} &
	\begin{tabular}{@{}ll}
		\href{mailto:gokul.narayanan@pm.me}{gokul.narayanan@pm.me}
		& +61 402 185 159 \\
		\href{https://github.com/narayanan-gokul}
		{github.com/narayanan-gokul} &
		\href{https://www.linkedin.com/in/gokul-narayanan-5a7681210/}
		{linkedin.com/in/gokul-narayanan} \\
	\end{tabular} \\
\end{tabularx}

\vspace{0.5em}
\rule{\textwidth}{2pt}

Enthusiastic and energetic team player who finds the greatest of joy in
helping peers.

% Education
\vspace{-0.5\baselineskip}
\section*{Education}
\hrule

\textbf{University of Sydney}, NSW, Australia \hfill
\textit{August 2025 -- Present} \\
Master of Computer Science \\

\vspace{-1\baselineskip}
\textbf{Fr. C Rodrigues Institute of Technology}, Maharashtra, India
\hfill \textit{May 2018 -- May 2022} \\
Bachelor of Engineering, Electrical \\
\vspace{-1.5\baselineskip}
\begin{itemize}[topsep=0pt, itemsep=0pt, partopsep=0pt, label=--]
	\item Served on the editing team for the Institute's newsletter.
	\item Hosted events such as the Annual Alumni meet and Welcome event
		for freshers.
\end{itemize}

\textbf{D.A.V. International School}, Maharashtra, India
\hfill \textit{July 2009 -- May 2018} \\
\vspace{-1.5\baselineskip}
\begin{itemize}[topsep=0pt, itemsep=0pt, partopsep=0pt, label=--]
	\item Served on the student council as the Deputy Head Boy (grade 8)
		and the Sports Captain (Grade 11).
\end{itemize}

% Experience
\vspace{-0.5\baselineskip}
\section*{Professional experience}
\hrule

\textbf{Freelance}, Remote, India \hfill \textit{July 2024 -- July 2025} \\
\textit{Backend developer} \\
\vspace{-1.5\baselineskip}
\begin{itemize}[label=--]
	\item Handled communication with project stakeholders served as an
		active member of the decision making process.
\end{itemize}

\textbf{Codeinbound LLP}, Remote, India \hfill \textit{May 2023 -- May 2024} \\
\textit{Software Development Engineer} \\
\vspace{-1.5\baselineskip}
\begin{itemize}[label=--]
	\item Responsible for onboarding new interns.
	\item In charge for daily standup for the backend team members.
	\item Collaborated with team members to solve problems together while
		managing the ownership of one of the product's core features.
\end{itemize}

\textbf{Codeinbound LLP}, Remote, India \hfill
\textit{February 2023 -- April 2023} \\
\textit{Software Development Engineer Intern} \\
\vspace{-1.5\baselineskip}
\begin{itemize}[label=--]
	\item Active participant in solving design problems.
	\item Consistently won the intern of the month certificate.
\end{itemize}

% Projects
\vspace{-0.5\baselineskip}
\section*{Miscellaneous experience}
\hrule
\begin{itemize}[label=--]
	\item Worked as a piano and guitar instructor for kids at Rhythm Music
		Hall, Mumbai.
	\item Tutored 11th grade students in Math.
\end{itemize}
% Skills
\vspace{-0.5\baselineskip}
\section*{Skills}
\hrule
\textbf{General}: Communication, Team work, Leadership \\
\textbf{Languages}: English (fluent), Hindi (fluent), Malayalam (Native) \\ 

% Interests
\vspace{-0.5\baselineskip}
\section*{Interests}
\hrule
Singing, Soccer, Driving, Photography

\end{document}
